BIOST 578, HW1
========================================================

**David Whitney's HW1**

1. Use the GEOmetabd package to find all HCV gene expression data using the Illumina platform submitted by an investigator at Yale. This should be done with a single query, showing the title, the GSE accession number, the GPL accession number and the manufacturer and the description of the platform used. 

**Answer**First we update and install the necessary packages for Bioconductor.
```{r}
#This can take a long time to download/install
source("http://bioconductor.org/biocLite.R")
biocLite(c("GEOmetadb", "GEOquery"))
library(GEOmetadb)
```

Now to get the 
```{r, eval=FALSE}
#This database download is particularly slow, so eval=FALSE for this code chunk
getSQLiteFile()
```

```{r, eval=TRUE}
# Make sure your current working directory contains GEOmetadb.sqlite
geo_con = dbConnect(SQLite(),'GEOmetadb.sqlite')
```

```{r}
# Join gse and gpl via the gse_gpl table
res = dbGetQuery(geo_con, "SELECT gse.title, gse.gse, gpl.gpl, gpl.manufacturer, gpl.technology, gse.contact FROM (gse JOIN gse_gpl ON gse.gse = gse_gpl.gse) j JOIN gpl ON j.gpl=gpl.gpl WHERE gpl.manufacturer LIKE '%Illumina%' AND gse.contact LIKE '%Yale%' AND gse.title LIKE '%Hepatitis C%'")
res
```

2. Reproduce your above query using the data.table package. Again, try to use a single line of code. [Hint: You first need to convert all db tables to data.table tables].

**Answer**

```{r}
# Working directory must contain the GEOmetadb.sqlite
library(data.table)

# Store each table for our query from the db in data.tables
gse.dt = data.table(dbGetQuery(geo_con, "SELECT gse.title, gse.gse, gse.contact FROM gse"))
gpl.dt = data.table(dbGetQuery(geo_con, "SELECT gpl.gpl, gpl.manufacturer, gpl.technology FROM gpl"))
gse_gpl.dt = data.table(dbGetQuery(geo_con, "SELECT gse_gpl.gse, gse_gpl.gpl FROM gse_gpl"))

# Set keys and then join the tables on gse
setkey(gse.dt,gse)
setkey(gse_gpl.dt,gse)
gse_gse_gpl.dt = gse.dt[gse_gpl.dt]

# Set keys and then join the new table and gpl table on gpl
setkey(gpl.dt,gpl)
setkey(gse_gse_gpl.dt,gpl)
merge.gse.gpl.dt = merge(gse_gse_gpl.dt, gpl.dt, all=TRUE)

# The final query for title, accession numbers, manufacturer, platform
merge.gse.gpl.dt[title %like% 'Hepatitis C' & manufacturer %like% 'Illumina' & contact %like% 'Yale']
```
