BIOST 578, HW1
========================================================

**This is your first homework due Tuesday Feb 4.**

1. Use the GEOmetabd package to find all HCV gene expression data using the Illumina platform submitted by an investigator at Yale. This should be done with a single query, showing the title, the GSE accession number, the GPL accession number and the manufacturer and the description of the platform used.

**Answer**First we update and install the necessary packages for Bioconductor.
```{r, eval=TRUE, cache=TRUE}
#This can take a long time to download/install
source("http://bioconductor.org/biocLite.R")
biocLite(c("GEOmetadb", "GEOquery"))
library(GEOmetadb)
```
```{r, eval=FALSE}
#This database download is particularly slow, so eval=FALSE for this code chunk
getSQLiteFile()
```

```{r}
geo_con = dbConnect(SQLite(),'GEOmetadb.sqlite')
```

```{r}
#Found pubmed_id on the GEO website
#This query has Illumina and Affymetrix manufacturers
res = dbGetQuery(geo_con, "SELECT gpl.title, gpl.gpl, gse.gse, gpl.manufacturer, gpl.description FROM (gse JOIN gse_gpl ON gse.gse = gse_gpl.gse) j JOIN gpl ON j.gpl=gpl.gpl WHERE gse.pubmed_id='23067362'")
```

2. Reproduce your above query using the data.table package. Again, try to use a single line of code. [Hint: You first need to convert all db tables to data.table tables].

```{r}
library(data.table)

```
